draft_final_assignment

### 2022-11-29 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@

##Creatung a dfm from the corpus
```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

#Do we also want to lemmatize and apply word stems??

# tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%

# tokens_wordstem() %>%
```

@@

```{r }
dfmat_115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 3)

@@

```{r }
dfmat_116 <- dfm(corpus_subset(corp, session == 116), remove = stopwords("english"), remove_punct = TRUE, 
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

@@

```{r }
dfmat_117 <- dfm(corpus_subset(corp, session == 117), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

@@

#Wordcloud comparing Democrats and Republicans
```{r }
#Need to get sponsor party data

dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$party) %>%
   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))

@@

mp15 <- textplot_wordcloud(modelpart15, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))
mp15

@@

#Wordcloud comparing Congresses
```{r }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$session) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

@@

ggplot(tfreq, aes(x=frequency, y=feature)) +
geom_col() + labs(title="Feature (word) frequency",
        x ="Frequency", y = "Feature") +
  theme_minimal() 
```
## Most common words (by session)

@@

```{r}
sims <- textstat_simil(dfm_corp, method="cosine")

@@

```{r }
df <- df %>%
  mutate(partisan = ifelse(cosponsor_D_perc > 0.5,"Dem", 
                       ifelse(cosponsor_D_perc < 0.5,"Rep",
                              ifelse(cosponsor_D_perc == 0.5,"Neutral", NA))))

corp <- corpus(df$summary)

dfmat2 <- corp %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm() %>%
  dfm_trim(min_termfreq = 5)

@@

colordict <- c( "Dem"="blue","Rep"="red", "Neutral"="yellow")

p <- ggplot(df, aes(x, y, fill=partisan)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) +
  theme_bw() +
  coord_fixed()

p
```

@@

```{r}
library(tidyr)
#tweet_sentiment$date <- as.Date(tweet_sentiment$created) 
summary_sentiment <- summary_sentiment %>%
  mutate(partisan = ifelse(cosponsor_D_perc > 0.5,"Dem", 
                       ifelse(cosponsor_D_perc < 0.5,"Rep",
                              ifelse(cosponsor_D_perc == 0.5,"Neutral", NA))))

wide_sentiment <- summary_sentiment %>%
  group_by(partisan, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = partisan, values_from = score) %>%
  select(-c("Neutral", "NA"))

@@

daily_sentiment <- days %>% 
  left_join(wide_sentiment) %>% 
  pivot_longer(cols = -date, names_to="partisan", values_to="score") %>%
  group_by(partisan) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

@@

ggplot(daily_sentiment, aes(date, colour=partisan)) +
  geom_point(aes(y=score), size=0.5) + 
  geom_line(aes(y=score7)) + theme_minimal()
```

>>>>

```{r}
ggplot(df, aes(x = cosponsor_D_perc)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.1, fill="blue") +
  labs(title="Density of bill cosposor party",
       x ="Cosponsor party composition", y = "Density", 
       caption = "Numbers represent proportion of cosponsors from Democratic party, 
       so 0.0 represents bills that were fully Republican and 1.0 represents 
       bills that were fully Democrat.") +
  theme_minimal()
```

@@

##Creatung a dfm from the corpus
```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
  tokens_wordstem() %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author")) %>%
  dfm()

#Do we also want to lemmatize and apply word stems??
# tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
# tokens_wordstem() %>%
```

@@

```{r }
dfmat_115 <- dfm_subset(dfmat, session == 115)

@@

```{r }
dfmat_116 <- dfm_subset(dfmat, session == 116)

@@

```{r }
dfmat_117 <- dfm_subset(dfmat, session == 117)

@@

#Wordcloud comparing Democrats and Republicans
```{r }
dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
                     corp$party) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))
```

@@

mp15 <- textplot_wordcloud(modelpart15, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))
mp15
```

@@

#Wordcloud comparing Congresses
```{r }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))
```

@@

ggplot(tfreq, aes(x=frequency, y=feature)) +
geom_col() + labs(title="Feature (word) frequency",
        x ="Frequency", y = "Feature") +
  theme_minimal() 
```
## Most common words by party

```{r}
#Republicans
dfmat_r <- dfm_subset(dfmat, party == "Republican")

tfreq_r <- dfmat_r %>%
  textstat_frequency() %>%
  head(20)

tfreq_r$feature <- factor(tfreq_r$feature, levels=tfreq_r$feature)

ggplot(tfreq_r, aes(x=frequency, y=feature)) +
geom_col() + labs(title="Feature (word) frequency for Republican Bills",
        x ="Frequency", y = "Feature") +
  theme_minimal() 
```

```{r}
#Democrats
dfmat_d <- dfm_subset(dfmat, party == "Democrat")

tfreq_d <- dfmat_d %>%
  textstat_frequency() %>%
  head(20)

tfreq_d$feature <- factor(tfreq_d$feature, levels=tfreq_d$feature)

ggplot(tfreq_d, aes(x=frequency, y=feature)) +
geom_col() + labs(title="Feature (word) frequency for Democrat Bills",
        x ="Frequency", y = "Feature") +
  theme_minimal() 
```

```{r}
party_corp <- corpus_subset(corp, 
                            party %in% c("Democrat", "Republican"))

# Create a dfm grouped by party
party_dfm <- tokens(party_corp, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
  tokens_wordstem() %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author", "may")) %>%
  tokens_group(groups = party) %>%
  dfm()

# Calculate keyness and determine Republican as target group
result_keyness <- textstat_keyness(party_dfm, target = "Republican")

# Plot estimated word keyness
textplot_keyness(result_keyness) 
```

## Most common words (by session)

@@

```{r}
sims <- textstat_simil(dfmat, method="cosine")

@@

```{r }
corp2 <- corpus(df$summary)

dfmat2 <- corp2 %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm() %>%
  dfm_trim(min_termfreq = 5)

@@

colordict <- c( "Democrat"="blue","Republican"="red", "Both"="yellow")

ggplot(df, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) +
  theme_bw()
```

@@

```{r}
summary_sentiment$party <- ifelse(summary_sentiment$cosponsor_D_perc > 0.66, "Democrat", ifelse(summary_sentiment$cosponsor_R_perc > 0.66, "Republican", "Both"))

wide_sentiment <- summary_sentiment %>%
  group_by(party, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = party, values_from = score) %>%
  select(-c("Both", "NA"))

@@

daily_sentiment <- days %>% 
  left_join(wide_sentiment) %>% 
  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
  group_by(party) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

@@

ggplot(daily_sentiment, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
```{r}
summary_sentiment$party_full <- ifelse(summary_sentiment$cosponsor_D_perc == 1.0, "Dem", ifelse(summary_sentiment$cosponsor_R_perc > 1.0, "Rep", "NA"))

wide_sentiment_full <- summary_sentiment %>%
  group_by(party, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = party, values_from = score) %>%
  select(-c("Both", "NA")) %>%
  drop_na(Democrat, Republican)

days_115 <- data.frame(date = seq(as.Date("2017-01-01"),as.Date("2018-12-31"),1))

daily_sentiment_115 <- days_115 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
  group_by(party) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

ggplot(daily_sentiment_115, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```

```{r}
days_116 <- data.frame(date = seq(as.Date("2019-01-01"),as.Date("2020-12-31"),1))

daily_sentiment_116 <- days_116 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
  group_by(party) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

daily_sentiment_116 %>% head()

ggplot(daily_sentiment_116, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
```{r}
days_117 <- data.frame(date = seq(as.Date("2021-01-01"),as.Date("2022-12-31"),1))

daily_sentiment_117 <- days_117 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
  group_by(party) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
